A contrast of meta and metafor packages for meta-analyses in R

### 2020-03-31 ms/2020/appendix_a.Rmd
done contrasts
app a updated - thanks Alex

A list of objects included in each package when loaded into the R environment.  
```{r appendix, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(kableExtra)

appendix <- read_csv("appendix.csv")
knitr::kable(appendix, "latex", booktabs = TRUE, longtable = TRUE) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "5cm") %>%
  column_spec(5, width = "2cm") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

>>>>

### A list of objects included in each package when loaded into the R environment.

```{r appendix, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(kableExtra)

appendix <- read_csv("appendix_2020.csv")
knitr::kable(appendix, "latex", booktabs = TRUE, longtable = TRUE) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "5cm") %>%
  column_spec(5, width = "2cm") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

### 2020-03-31 ms/2020/ms.Rmd
app a updated - thanks Alex

>>>>

Models are powerful and typically necessary tools to better understand data. Conservatively, a model is a mechanism to explore uncertainty and assign weight to an observed pattern in the data [@RN6117}. Any statistical test albeit simple is thus a model to help describe a trend and difference. Less generously, it has been proposed that all models are wrong but that some are useful [@RN6467]. In this vein, it is not unreasonable to examine the outputs of similar packages to
